Report

### 2022-06-14 manuscript.Rmd

bibliography      : ["references.bib"]

@@

To examine performance in a range of realistic scenarios,
several design factors were manipulated:
The population effect size $\rho \in (-0.1, 0, 0.1, 0.2)$,
the sample size per group $n \in (20, 80, 200, 500)$,
the number of groups $k \in (2, 3, 10)$, where 2 is the minimum number of groups and 10 is a very large number of groups,
and the reliability of the two correlated variables, $\alpha \in (0.6, 0.8, 1.0)$, where 0.6 is the lowest reliability conventionally considered to be acceptable, and 1 represents perfect reliability, as is assumed when analyzing correlations between observed items or scale scores.
The design factors combined to produce `r out$conditions` unique conditions.
For all simulation conditions, 1000 data sets were generated.

```{r, echo = F}
library(data.table) # load in libraries
library(DT)
library(ggplot2)
rename <- c("prodbf" = "PBF", "gpbf" = "gPBF", "tbf" = "TBF", "ipd" = "IPD", "rma" = "RMA", "allsig" = "VC")

@@

We examined the effect of simulation conditions on overall accuracy.

```{r tabeffect, echo = FALSE}
tab <- read.csv("effect_of_conditions.csv", stringsAsFactors = FALSE)
tab <- tab[, !grepl("(gpbf|tbf)", names(tab))]
tab <- tab[, c("condition", "prodbf_ic", "rma", "ipd", "allsig", "prodbf_ic.vs..rma", "ipd.vs..prodbf_ic", "allsig.vs..prodbf_ic")]
names(tab) <-  c("Factor", "PBF", "RMA", "IPD", "VC", "vs RMA", "vs IPD", "vs VC")

knitr::kable(tab, digits = 2, caption = "Partial eta squared of the effect of each design factor on accuracy for each algorithm and for the difference between PBF and all other algorithms (e.g., vs RMA).")
```
PBF performance was most impacted by sample size $n$, followed by the number of groups $k$, and reliability.
<!-- should we also test for interaction effects? I seem to remember that there were some interesting effects of errorsd*k and n*k -->
<!-- CJ: I don't think so, that might be more relevant for one of the papers that focused on the simulation study. For this tutorial, a simpler sim is fine. -->

>>>>

bibliography      : ["product_bayes.bib"]

@@

To examine performance in a range of realistic scenarios,
several design factors were manipulated:
The sample size per group $n \in (20, 80, 200, 500)$,
the number of groups $k \in (2, 3, 10)$, where 2 is the minimum number of groups and 10 is a very large number of groups,
and the reliability of the two correlated variables, $\alpha \in (0.6, 0.8, 1.0)$, where 0.6 is the lowest reliability conventionally considered to be acceptable, and 1 represents perfect reliability, as is assumed when analyzing correlations between observed items or scale scores.
The design factors combined to produce `r out$conditions` unique conditions.
For all simulation conditions, 1000 data sets were generated.

```{r, echo = F}
library(data.table) # load in libraries
library(DT)
library(ggplot2)
# rename <- c("prodbf" = "PBF", "gpbf" = "gPBF", "tbf" = "TBF", "ipd" = "IPD", "rma" = "RMA", "allsig" = "VC")

@@

We examined the effect of simulation conditions on overall accuracy.
```{r tabeffect, echo = FALSE}
tab <- read.csv("effect_of_conditions.csv", stringsAsFactors = FALSE)
tab <- tab[, !grepl("(gpbf|tbf)", names(tab))]
tab <- tab[, grepl("^\\w+$", names(tab)) | (grepl("\\.{2}", names(tab)) & grepl("PBF", names(tab)))]
names(tab)[grepl("\\.{2}", names(tab))] <- paste0("vs ", gsub("(\\.|PBF|vs)", "", names(tab)[grepl("\\.{2}", names(tab))]))
knitr::kable(tab, digits = 2, caption = "Partial eta squared of the effect of each design factor on accuracy for each algorithm and for the difference between PBF and all other algorithms (e.g., vs RMA).")
```
PBF performance was most impacted by sample size $n$, followed by the number of groups $k$, and reliability.
<!-- should we also test for interaction effects? I seem to remember that there were some interesting effects of errorsd*k and n*k -->
<!-- CJ: I don't think so, that might be more relevant for one of the papers that focused on the simulation study. For this tutorial, a simpler sim is fine. -->
